### 2022-04-29 GB_Simulation_3Species.Rmd
small updates

#profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

#moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata")
moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata_res2")

@@

@@

#   #rebuild package
devtools::build()

@@

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-toy/20 year moveCov matrices/Final/Increase_temp_20yr_LargerTempVA7.RData")

  #this starts the profiling
library(profvis)

profvis({

@@

@@

result <- parallel::parLapply(cl,1:6,run_simulation)
parallel::stopCluster(cl)

>>>>

#profvis::profvis({
#original settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 10472, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

#increasing population
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 40000, "b" = 4301*10, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 45000 , "b" = 10472*6, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 100000, "b" = 40530*10, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.1, "spp3" = .334+.45), #NEED F
                   K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

#moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata")

#Constant temp
moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_ConstTemp_HaddockStrata_res2")

#increasing temp
moveCov <- readRDS(file="20 year moveCov matrices/GeorgesBank/GB_22yr_IncrTemp_HaddockStrata_res2")

@@

  #this might track progress. If not check here: https://cran.r-project.org/web/packages/pbapply/pbapply.pdf
 system(paste("echo 'now processing:",x,"'"))

@@

#   #rebuild package
#devtools::build()

@@

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_ConstTemp_environment.RData")

  #this starts the profiling
# library(profvis)
# 
# profvis({

@@

 return(res)

@@

result <- parallel::parLapply(cl,1:100,run_simulation)
parallel::stopCluster(cl)
